A Switching Planner for Combined Task and Observation Planning

### 2010-11-19 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/moritz_2011.tex
initial state

The syntax and semantics for describing initial state distributions in
DTPDDL is taken verbatim from PPDDL. It is useful to present that
factored tree-like structure here, in order to aid our discussion of
sequential planning in POMDP determinisations. The distribution is
expressed in a tree-like structure of terms. Each term is either: (1)
atomic, e.g., $(=(\pp{location}~\pp{box})~\pp{office})$, (2)
probabilistic, e.g., $(\pp{probabilistic}~p_1 (T_1) .. p_n (T_n))$, or
(3) a conjunct over probabilistic and atomic terms. The root term is
conjunctive, and the leaves are atomic. For example, the starting
distribution for $\pp{R2D2}$ might be described thusly:

@@

\noindent The interpretation of such an expression can be given
according to a recursive descent.

>>>>

The syntax and semantics for describing initial state distributions in
DTPDDL is taken verbatim from PPDDL. It is useful to present that
factored tree-like structure here, in order to aid our discussion of
sequential planning in POMDP determinisations. The distribution is
expressed in a tree-like structure of terms. Each term is either: (1)
atomic, e.g., $(=(\pp{location}~\pp{box})~\pp{office})$, (2)
probabilistic, e.g., $(\pp{probabilistic}~p_1 (T_1) .. p_n (T_n))$
where $T_i$ are conjunctive, or (3) a conjunct over probabilistic and
atomic terms. The root term is always conjunctive, and the leaves are
atomic. For example, the starting distribution for $\pp{R2D2}$ might
be described thusly:

@@

\noindent The interpretation of such an expression can be given
according to a recursive descent. Here, an atom is visited as soon as
its conjunctive parent is visited, and a conjunctive term is visited
if all its immediate subterms are visited. A probabilistic term is
visited if exactly one of its subterms, $T_i$, is visited. Each valid
visitation of the root term according to this recursive definition
encapsulates a starting state, along with the probability it
occurs. The former corresponds to the union of all visited atoms, and
the latter corresponds to the product of $p_i$ entries on the visited
subterms of probabilistic elements. Making these ideas concrete, our
example yields the following flat state distribution:

\begin{tabular}{cccc}
\hline
Probability & (is-in R2D2)  & (is-in box)  & (is-in cup) \\
\hline
.24 & kitchen & office & office \\
.06 & kitchen & kitchen & office \\
.56 & kitchen & office & kitchen \\
.14 & kitchen & kitchen & kitchen \\
\hline
\end{tabular}
